\mythesistitle

### 2011-11-26 src/synopsis.tex
another bunch of last minute changes. THE NEXT COMMIT WILL BE THE FINAL FUCKING ONE!

\usepackage{times} 
\usepackage{t1enc}
\usepackage{../lib/mylatexlib}

@@

@@

% \tnote{TBD: DELETE IF WE RUN OUT OF SPACE}
% \begin{singlespace}
% \tableofcontents
% \thispagestyle{empty}
% \listoffigures
% \addcontentsline{toc}{chapter}{LIST OF FIGURES}
% \listoftables
% \addcontentsline{toc}{chapter}{LIST OF TABLES}
% \end{singlespace}

@@

\section{Introduction}
\label{sec:intro}
\vspace{\secfirstparatrim}
\tnote{set context: COP - generalization - TPL - no opt. just 2 or 3
  sentences. use the space that the illustration does.}
% \tnote{testing 1 2 3...}
% \tnote[bogus1]{testing 1 2 3...}
% \tnote[bogus2]{testing 1 2 3...}
% \tnote[GTC]{testing 1 2 3...}
% \tnote[bogus4]{testing 1 2 3...}
% \tnote[TH]{testing 1 2 3...}

\subsection{Illustration of the problem}
\label{sec:problem}
\vspace{\secfirstparatrim}
% \def \LLL {{\em ``{\bf L}aughing with Kafka''}} 
% \def \GGG {{\em ``{\bf G}irl with Curious Hair''}} 
% \def \BBB {{\em ``{\bf B}rief Interviews with Hideous Men''}}
% \def \TTT {{\em ``Everything and More: A Compact His{\bf T}ory of Infinity''}} 
% \def \xLLL {{\bf L}}
% \def \xGGG {{\bf G}} 
% \def \xBBB {{\bf B}}
% \def \xTTT {{\bf T}}

%{\bf L}aughing {\bf G}irl {\bf B}rief {\bf T}his

% \def \LLL {{\em ``{\bf L}aughing with Kafka''}} 
% \def \GGG {{\em ``Brief {\bf I}nterviews with Hideous Men''}} 
% \def \BBB {{\em ``Broom of the {\bf S}ystem''}}
% \def \TTT {{\em ``Everything and More: {\bf A} Compact History of Infinity''}}

% \def \xLLL {{\bf L}}
% \def \xGGG {{\bf I}} 
% \def \xBBB {{\bf S}}
% \def \xTTT {{\bf A}}

% \def \LLL {{\em ``{\bf B}rief Interviews with Hideous Men''}} 
% \def \GGG {{\em ``The String {\bf T}heory''}} 
% \def \BBB {{\em ``[{\bf W}]Rhetoric and the Math Melodrama''}}
% \def \TTT {{\em ``{\bf F}ate, Time, and Language: An Essay on Free Will''}}
\def \LLL {{\em ``$\mathbb{B}$rief Interviews with Hideous Men''}}
\def \GGG {{\em ``The String $\mathbb{T}$heory''}} 
\def \BBB {{\em ``[$\mathbb{W}$]Rhetoric and the Math Melodrama''}}
\def \TTT {{\em ``$\mathbb{F}$ate, Time, and Language: An Essay on Free Will''}}

% \def \xLLL {{\bf B}}
% \def \xGGG {{\bf T}} 
% \def \xBBB {{\bf W}}
% \def \xTTT {{\bf F}}
\def \xLLL {\mathbb{B}}
\def \xGGG {\mathbb{T}} 
\def \xBBB {\mathbb{W}}
\def \xTTT {\mathbb{F}}

%{{\em ``Everything and More: A Compact History of In{\bf F}inity''}} 
% {{\em ``Broom of {\bf T}he System''}} % {Consider the Lobster}
% {{\em ``God Bless You, Mr. {\bf F}ranzen''}}
% {{\em ``{\bf L}aughing with Kafka''}} 
% {{\em ``{\bf G}irl with Curious Hair''}} 
% {{\em ``Consider the {\bf L}obster|}}
% {{\em ``{\bf G}od Bless You, Mr. Franzen''}}
% {{\em ``{\bf T}ennis, Trigonometry,
%                                Tornadoes: A Midwestern  Boyhood''}}
% {{\em ``{\bf T}his is Water''}} %
% {\em {{\bf T}he Pale King}}

\def \Pa {{\em {\bf Pa}tricia}} 
\def \Pi {{\em {\bf Pi}gpen}} %{{\em {\bf Ma}rcie}}
\def \Sn {{\em {\bf Sn}oopy}}
\def \Wo {{\em {\bf Wo}odstock}}
\def \Vi {{\em {\bf Vi}olet}} 
\def \Li {{\em {\bf Li}nus}} 
\def \Ch {{\em {\bf Ch}arlie}}
\def \Sa {{\em {\bf Sa}lly}}
\def \Fr {{\em {\bf Fr}anklin}}  %{{\em {\bf Re}run}} 
\def \Sc {{\em {\bf Sc}hr{\"o}eder}} 
\def \Lu {{\em {\bf Lu}cy}}

\def \xPa {{\bf Pa}} 
\def \xPi {{\bf Pi}} 
\def \xSn {{\bf Sn}}
\def \xWo {{\bf Wo}}
\def \xVi {{\bf Vi}} 
\def \xLi {{\bf Li}} 
\def \xCh {{\bf Ch}}
\def \xSa {{\bf Sa}}
\def \xFr {{\bf Fr}}
\def \xSc {{\bf Sc}} 
\def \xLu {{\bf Lu}}

\def \residenceblock {{\em Infinite Loop}}

\def \WSI {{\em Wallace Studies Institute}}

\def \coneohone {{\em ``Influence of post modernism in Wallace's work''}}
\def \coneohtwo {{\em ``A study on fragmented prose method''}}

@@

\begin{table}[htbp]
  \centering
{
  \begin{tabular}{rcl}
    $U $&$=$&$ \{\xPa,\; \xPi,\; \xSn,\; \xWo,\; \xVi,\; \xLi,\; \xCh,\;
    \xSa,\; \xFr,\; \xSc,\; \xLu\}$\\
    $\cF $&$=$&$ \{\xLLL, \xGGG, \xBBB, \xTTT\}$\\
    $\xLLL $&$=$&$ \{\xCh,\;  \xSa,\;  \xFr,\;  \xSc,\;  \xLu \}$\\
    $\xGGG $&$=$&$ \{\xPa,\;  \xPi,\;  \xVi,\;  \xCh \}$\\
    $\xBBB $&$=$&$ \{\xSn,\;  \xPi,\;  \xWo \}$\\
    $\xTTT $&$=$&$ \{\xVi,\;  \xLi,\;  \xCh,\;  \xFr \}$\\
    $n $&$=$&$ |U| = 11$\\
    $m $&$=$&$ |\cF| = 4$      
  \end{tabular}
}
  \caption{\figtabsize Students and study groups in \WSI}
  \label{tab:wsigroups}
\end{table}

% The administration faces a small challenge with their
% accommodation. 
The campus has a residential area {\residenceblock} that has $n$
single occupancy apartments reserved for the study groups'
accommodation.  All these apartments are located such that the streets
connecting them do {\em not} form loops. Fig~\ref{fig:streetmap} shows
the street map for {\residenceblock}. It may be noted that as a graph,
it classifies as a tree.

@@

An intuitive approach to this problem would be to first find the paths
that each study group decides to inhabit and then refine the
allocation to individual students. A feasible allocation of exclusive
routes to study groups is illustrated in Fig~\ref{fig:streetmappath}
and the students' allocation of apartments that obeys this route
allocation is also shown\tnote[TH]{in
  Fig~ref::fig:streetmappathpeople}. How this is algorithmically
computed is the focus of this thesis.

@@

% \begin{figure}[t]%[htbp]
%   \centering
%   \includegraphics[scale=0.3]{../img/2_infinite_loop_BTWF.png}
%   \caption{{\residenceblock} street map with study group routes
%     allocated. Routes are color coded as follows: red for
%     \textcolor{red}{$\xLLL$} group, blue for \textcolor{blue}{$\xGGG$}
%     group, orange for \textcolor{YellowOrange}{$\xBBB$} group, green for
%     \textcolor{green}{$\xTTT$} group}
%   \label{fig:streetmappath}
% \end{figure}
% \begin{figure}[t] % [h]
%   \centering
%   \includegraphics[scale=0.5]{../img/3_infinite_loop.png}
%   \caption{Individual allocation of apartments to students in
%     {\residenceblock} that meets the requirements stated before.}
%   \label{fig:streetmappathpeople}
% \end{figure}
%%%%%%%%%%%% END THESIS UNCOMMENT %%%%%%%%%%%%
% \begin{figure}[htbp] %[t]%
%  \centering
%   (a) \includegraphics[scale=0.2]{../img/1_infinite_loop.png}
%   (b) \includegraphics[scale=0.2]{../img/2_infinite_loop_BTWF.png}
%  \label{fig:streetmap}
%   \caption{\figtabsize (a) {\residenceblock} street map (b) {\residenceblock} street map with study group routes
%     allocated. Routes are color coded as follows: red for
%     \textcolor{red}{$\xLLL$} group, blue for \textcolor{blue}{$\xGGG$}
%     group, orange for \textcolor{YellowOrange}{$\xBBB$} group, green for
%     \textcolor{green}{$\xTTT$} group}
% \end{figure}
% \begin{figure}[htbp] %[t]%
%   \centering
%   \includegraphics[scale=0.3]{../img/3_infinite_loop.png}
%   \caption{\figtabsize Individual allocation of apartments to students in
%     {\residenceblock} that meets the requirements stated before.}
%   \label{fig:streetmappathpeople}
% \end{figure}

@@

\section{Summary of results}
\label{sec:results}
\vspace{\secfirstparatrim}
% We address the computation of TPL\footnote{Tree Path Labeling} for a
% given hypergraph\footnote{The term {\em hypergraph} is used instead
%   {\em set systems} are used interchangably in this
%   section. Hypergraphs that have TPLs on some target tree are called
%   {\em path hypergraphs}.} and target tree in this research. However
% optimization problems in TPL, akin to problems in
% Section~\ref{sec:optcop} for COP, is outside the scope of this thesis.
As we saw earlier by the result in \cite{nsnrs09}, pairwise
intersection cardinality preservation is necessary and sufficient for
an interval assignment to be feasible for a given
hypergraph\footnote{A {\em hypergraph} is an alternate representation
  of a set system and will be used through out this section.} and thus
is a characterization for COP. In our work we extend this
characterization and find that trio-wise intersection cardinality
preservation makes a tree path labeling (TPL) feasible, which is a
generalization of the COP problem. This problem, {\FTPL}\footnote{A
  {\em tree path labeling} $\cl$ is a bijection of paths from the
  target tree $T$ to the hyperedges in given hypergraph $\cF$.}, is
defined as follows.\\

\begin{minipage}[h]{5in}
  % \begin{singlespace}
  {\large \FTPL}\\
  % \hline
  \begin{tabular}[t]{l|l}
    {\tt Input} & 
    \begin{minipage}[t]{\probdefwidth}
      A hypergraph $\cF$ with vertex set $U$, a tree $T$ and a
      bijection $\cl$~$:$~$\cF \rightarrow \cP$, where $\cP$ is a set
      of paths from $T$.\\
    \end{minipage}\\
    {\tt Question} &
    \begin{minipage}[t]{\probdefwidth}
      Does there exist a bijection $\phi$~$:$~$U \rightarrow V(T)$
      such that $\phi$ when applied on any hyperedge in $\cF$ will
      give
      the path mapped to it by the given tree path labeling $\cl$.\\
      { i.e., $\cl(S) = \{\phi(x) \mid x \in S\}$, for every hyperedge
        $S \in \cF$.}
    \end{minipage}\\
  \end{tabular}
  % \end{singlespace}
\end{minipage}\\

@@

Aside from checking if a given TPL is feasible, we also solve the
problem of computing a feasible TPL for a given hypergraph and target
tree, if one exists. This problem, {\CFTPL}, is defined as follows. \\

\begin{minipage}[h]{5in}
  % \begin{singlespace}
  {\large \CFTPL}\\
  % \hline
  \begin{tabular}[t]{l|l}
    {\tt Input} & 
    \begin{minipage}[t]{\probdefwidth}
      A hypergraph $\cF$ with vertex set $U$ and a tree $T$.\\
    \end{minipage}\\

    {\tt Question} &
    \begin{minipage}[t]{\probdefwidth}
      Does there exist a set of paths $\cP$ from $T$ and a bijection
      $\cl$~$:$~$\cF \rightarrow \cP$, such that {\FTPL} returns {\bf
        true} on $(\cF, T, \cl)$.
    \end{minipage}\\
  \end{tabular}
  % \end{singlespace}
\end{minipage}\\

\def \CFTPLKTREE {\sc Compute $k$-subdivided Star Path Labeling}

We present a polynomial time algorithm for {\CFTPL} when the target
tree $T$ belongs to a special class of trees called {\em
  $k$-subdivided stars} and when the hyperedges in the hypergraph
$\cF$ have at most $k+2$ vertices. The examples of $k$-subdivided
stars given in Figure~\ref{fig:ksubstar} makes the definition clear.

%This problem, {\CFTPLKTREE}, is defined as follows. \\
\begin{figure}[htbp]
  \centering
  (a) \includegraphics[scale=0.4]{../img/star.pdf}
  (b) \includegraphics[scale=0.4]{../img/kstar.pdf}
  \caption{\figtabsize Examples of $k$-subdivided stars. (a) $k = 0$ (b) $k = 2$ }
  \label{fig:ksubstar}
\end{figure}

\begin{minipage}[h]{5in}
  % \begin{singlespace}
  {\large \CFTPLKTREE}\\
  % \hline
  \begin{tabular}[t]{l|l}
    {\tt Input} & 
    \begin{minipage}[t]{\probdefwidth}
      A hypergraph $\cF$ with vertex set $U$ such that every hyperedge
      $S \in \cF$ is of cardinality atmost $k+2$ and a $k$-subdivided
      star $T$.\\
    \end{minipage}\\

    {\tt Question} &
    \begin{minipage}[t]{\probdefwidth}
      Does there exist a set of paths $\cP$ from $T$ and a bijection
      $\cl$~$:$~$\cF \rightarrow \cP$, such that {\FTPL} returns {\bf
        true} on $(\cF, T, \cl)$.
    \end{minipage}\\
  \end{tabular}
  % \end{singlespace}
\end{minipage}\\

In spite of this
restricted case we consider, we believe that our results are of
significant interest in understanding the nature of {\sc Graph
  Isomorphism} which is polynomial time solvable in interval graphs
while being hard on path graphs\cite{kklv10}.

>>>>

\usepackage{times} 
\usepackage{t1enc}
\usepackage{boxedminipage}
\usepackage{../lib/mylatexlib}

@@

% \def \LLL {{\em ``{\bf L}aughing with Kafka''}} 
% \def \GGG {{\em ``{\bf G}irl with Curious Hair''}} 
% \def \BBB {{\em ``{\bf B}rief Interviews with Hideous Men''}}
% \def \TTT {{\em ``Everything and More: A Compact His{\bf T}ory of Infinity''}} 
% \def \xLLL {{\bf L}}
% \def \xGGG {{\bf G}} 
% \def \xBBB {{\bf B}}
% \def \xTTT {{\bf T}}
%%%%%%
% \def \LLL {{\em ``{\bf L}aughing with Kafka''}} 
% \def \GGG {{\em ``Brief {\bf I}nterviews with Hideous Men''}} 
% \def \BBB {{\em ``Broom of the {\bf S}ystem''}}
% \def \TTT {{\em ``Everything and More: {\bf A} Compact History of Infinity''}}
% \def \xLLL {{\bf L}}
% \def \xGGG {{\bf I}} 
% \def \xBBB {{\bf S}}
% \def \xTTT {{\bf A}}
%%%%%%
\def \LLL {{\em ``$\mathbb{B}$rief Interviews with Hideous Men''}}
\def \GGG {{\em ``The String $\mathbb{T}$heory''}} 
\def \BBB {{\em ``[$\mathbb{W}$]Rhetoric and the Math Melodrama''}}
\def \TTT {{\em ``$\mathbb{F}$ate, Time, and Language: An Essay on Free Will''}}
\def \xLLL {\mathbb{B}}
\def \xGGG {\mathbb{T}} 
\def \xBBB {\mathbb{W}}
\def \xTTT {\mathbb{F}}
% {{\em ``{\bf B}rief Interviews with Hideous Men''}} 
% {{\em ``The String {\bf T}heory''}} 
% {{\em ``[{\bf W}]Rhetoric and the Math Melodrama''}}
% {{\em ``{\bf F}ate, Time, and Language: An Essay on Free Will''}}
% {{\em ``Everything and More: A Compact History of In{\bf F}inity''}} 
% {{\em ``Broom of {\bf T}he System''}} 
% {{\em ``Consider the Lobster''}}
% {{\em ``God Bless You, Mr. {\bf F}ranzen''}}
% {{\em ``{\bf L}aughing with Kafka''}} 
% {{\em ``{\bf G}irl with Curious Hair''}} 
% {{\em ``Consider the {\bf L}obster''}}
% {{\em ``{\bf G}od Bless You, Mr. Franzen''}}
% {{\em ``{\bf T}ennis, Trigonometry,
%                                Tornadoes: A Midwestern  Boyhood''}}
% {{\em ``{\bf T}his is Water''}}
% {{\em ``{\bf T}he Pale King''}}

\def \Pa {{\em {\bf Pa}tricia}} 
\def \Pi {{\em {\bf Pi}gpen}}
\def \Sn {{\em {\bf Sn}oopy}}
\def \Wo {{\em {\bf Wo}odstock}}
\def \Vi {{\em {\bf Vi}olet}} 
\def \Li {{\em {\bf Li}nus}} 
\def \Ch {{\em {\bf Ch}arlie}}
\def \Sa {{\em {\bf Sa}lly}}
\def \Fr {{\em {\bf Fr}anklin}} 
\def \Sc {{\em {\bf Sc}hr{\"o}eder}} 
\def \Lu {{\em {\bf Lu}cy}}
\def \xPa {{\bf Pa}} 
\def \xPi {{\bf Pi}} 
\def \xSn {{\bf Sn}}
\def \xWo {{\bf Wo}}
\def \xVi {{\bf Vi}} 
\def \xLi {{\bf Li}} 
\def \xCh {{\bf Ch}}
\def \xSa {{\bf Sa}}
\def \xFr {{\bf Fr}}
\def \xSc {{\bf Sc}} 
\def \xLu {{\bf Lu}}
\def \residenceblock {{\em Infinite Loop}}
\def \WSI {{\em Wallace Studies Institute}}
\def \coneohone {{\em ``Influence of post modernism in Wallace's work''}}
\def \coneohtwo {{\em ``A study on fragmented prose method''}}

@@

@@

\section{Introduction}
\label{sec:intro}
\vspace{\secfirstparatrim}

Consecutive ones property is a non-trivial property of binary matrices
that has been studied widely in the literature for over past 50
years. Detection of COP in a matrix is possible efficiently and there
are several algorithms that achieve the same. This thesis documents
the work done on an extension of COP extended from the equivalent
interval assignment problem in \cite{nsnrs09}. These new results
rigorously prove a natural extension (to trees) of their
characterization as well as makes connections to graph isomorphism,
namely path graph isomorphism.

% \tnote{testing 1 2 3...}
% \tnote[bogus1]{testing 1 2 3...}
% \tnote[bogus2]{testing 1 2 3...}
% \tnote[GTC]{testing 1 2 3...}
% \tnote[bogus4]{testing 1 2 3...}
% \tnote[TH]{testing 1 2 3...}

\subsection{Illustration of the problem}
\label{sec:problem}
\vspace{\secfirstparatrim}

@@

\begin{table}[htbp]
  \centering
  { \footnotesize
  \begin{tabular}{rcl}
    $U $&$=$&$ \{\xPa,\; \xPi,\; \xSn,\; \xWo,\; \xVi,\; \xLi,\; \xCh,\;
    \xSa,\; \xFr,\; \xSc,\; \xLu\}$\\
    $\cF $&$=$&$ \{\xLLL, \xGGG, \xBBB, \xTTT\}$\\
    $\xLLL $&$=$&$ \{\xCh,\;  \xSa,\;  \xFr,\;  \xSc,\;  \xLu \}$\\
    $\xGGG $&$=$&$ \{\xPa,\;  \xPi,\;  \xVi,\;  \xCh \}$\\
    $\xBBB $&$=$&$ \{\xSn,\;  \xPi,\;  \xWo \}$\\
    $\xTTT $&$=$&$ \{\xVi,\;  \xLi,\;  \xCh,\;  \xFr \}$\\
    $n $&$=$&$ |U| = 11$\\
    $m $&$=$&$ |\cF| = 4$      
  \end{tabular}
}
  \caption{\figtabsize Students and study groups in \WSI}
  \label{tab:wsigroups}
\end{table}

% The administration faces a small challenge with their
% accommodation. 
The campus has a residential area {\residenceblock} that has $n$
single occupancy apartments reserved for the study groups'
accommodation.  All these apartments are located such that the streets
connecting them do {\em not} form
loops. Fig~\ref{fig:streetmappathpeople} \tnote[TH]{fig:streetmap}
shows the street map for {\residenceblock}. It may be noted that as a
graph, it classifies as a tree.

\begin{table}[htbp]
  \centering
  {\footnotesize    
    \begin{tabular}{l||l}
      \begin{tabular}{rcl}
        $T $&$=$&$ \text{\em Street map tree of \residenceblock}$\\
        $V(T) $&$=$&$ \{ 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11 \}$\\
        % $\phi^{-1}(V(T)) $&$=$&$ \{ \xSa,\; \xPi,\; \xFr,\; \xWo,\;
        % \xCh,\; \xVi,\;
        % \xPa,\; \xSn,\; \xLu,\; \xLi,\; \xSc \}$\\
        $\cP $&$=$&$ \{R\xLLL, R\xGGG, R\xBBB, R\xTTT\}$\\
        $R\xLLL $&$=$&$ \{9, 1, 5, 3, 11\}$\\
        $R\xGGG $&$=$&$ \{7, 2, 6, 5\}$\\
        $R\xBBB $&$=$&$ \{8, 2, 4 \}$\\
        $R\xTTT $&$=$&$ \{10, 6, 5, 3\}$\\
        $n $&$=$&$ |V| = 11$\\
        $m $&$=$&$ |\cP| = 4$\\\\
        $\cl $&$=$& {\em Study group to route mapping}\\        
        $\cl(\mathbb{X}) $&$=$&  $R\mathbb{X}$ for all $\mathbb{X} \in
        \cF$
      \end{tabular} & 
      \begin{tabular}{c}
       {\em Apartment allocation }($\phi$)\\
                    \begin{tabular}{c|c}                      
                      1  & \xSa\\
                      2  & \xPi\\
                      3  & \xFr\\
                      4  & \xWo\\
                      5  & \xCh\\
                      6  & \xVi\\
                      7  & \xPa\\
                      8  & \xSn\\
                      9  & \xLu\\
                      10 & \xLi\\
                      11 & \xSc                     
                    \end{tabular}
      \end{tabular}\\
    \end{tabular}
  }
  \caption{\figtabsize A solution to study group accommodation problem}
  \label{tab:iltree}
\end{table}

@@

An intuitive approach to this problem would be to first find the paths
that each study group decides to inhabit and then refine the
allocation to individual students. A feasible allocation of exclusive
routes to study groups is illustrated in
Fig~\ref{fig:streetmappathpeople} \tnote[TH]{fig:streetmappath} and
the students' allocation of apartments that obeys this route
allocation is also shown. Table~\ref{tab:iltree} shows the same
solution set theoretically.  How this is algorithmically computed is
the focus of this thesis.

@@

% \begin{figure}[t]%[htbp]
%   \centering
%   \includegraphics[scale=0.3]{../img/2_infinite_loop_BTWF.png}
%   \caption{{\residenceblock} street map with study group routes
%     allocated. Routes are color coded as follows: red for
%     \textcolor{red}{$\xLLL$} group, blue for \textcolor{blue}{$\xGGG$}
%     group, orange for \textcolor{YellowOrange}{$\xBBB$} group, green for
%     \textcolor{green}{$\xTTT$} group}
%   \label{fig:streetmappath}
% \end{figure}
% \begin{figure}[t] % [h]
%   \centering
%   \includegraphics[scale=0.5]{../img/3_infinite_loop.png}
%   \caption{Individual allocation of apartments to students in
%     {\residenceblock} that meets the requirements stated before.}
%   \label{fig:streetmappathpeople}
% \end{figure}
%%%%%%%%%%%% END THESIS UNCOMMENT %%%%%%%%%%%%
% \begin{figure}[htbp] %[t]%
%  \centering
%   (a) \includegraphics[scale=0.2]{../img/1_infinite_loop.png}
%   (b) \includegraphics[scale=0.2]{../img/2_infinite_loop_BTWF.png}
%  \label{fig:streetmap}
%   \caption{\figtabsize (a) {\residenceblock} street map (b) {\residenceblock} street map with study group routes
%     allocated. Routes are color coded as follows: red for
%     \textcolor{red}{$\xLLL$} group, blue for \textcolor{blue}{$\xGGG$}
%     group, orange for \textcolor{YellowOrange}{$\xBBB$} group, green for
%     \textcolor{green}{$\xTTT$} group}
% \end{figure}
\begin{figure}[htbp] %[t]%
  \centering
  \includegraphics[scale=0.3]{../img/3_infinite_loop.png}
  \caption{\figtabsize Individual allocation of apartments to students
    in {\residenceblock} that meets the requirements stated before.
    The routes are color coded as follows: red for
    \textcolor{red}{$\xLLL$} group, blue for \textcolor{blue}{$\xGGG$}
    group, orange for \textcolor{YellowOrange}{$\xBBB$} group, green
    for \textcolor{green}{$\xTTT$} group. {\tiny {\em Peanuts images {\copyright} Charles
    Schulz}}}
  \label{fig:streetmappathpeople}
\end{figure}

@@

\section{Summary of results}
\label{sec:results}
\vspace{\secfirstparatrim}
% We address the computation of TPL\footnote{Tree Path Labeling} for a
% given hypergraph\footnote{The term {\em hypergraph} is used instead
%   {\em set systems} are used interchangably in this
%   section. Hypergraphs that have TPLs on some target tree are called
%   {\em path hypergraphs}.} and target tree in this research. However
% optimization problems in TPL, akin to problems in
% Section~\ref{sec:optcop} for COP, is outside the scope of this thesis.
As we saw earlier by the result in \cite{nsnrs09}, pairwise
intersection cardinality preservation is necessary and sufficient for
an interval assignment to be feasible for a given
hypergraph\footnote{A {\em hypergraph} is an alternate representation
  of a set system and will be used through out this section.} and thus
is a characterization for COP. In our work we extend this
characterization and find that trio-wise intersection cardinality
preservation makes a tree path labeling (TPL) feasible, which is a
generalization of the COP problem. This problem, {\FTPL}\footnote{A
  {\em tree path labeling} $\cl$ is a bijection of paths from the
  target tree $T$ to the hyperedges in given hypergraph $\cF$.}, is
defined as follows.

%\begin{tabular}[t]{c}
{\small
\begin{minipage}[h]{5in}
 % \begin{singlespace}
 \vspace{2mm}
 {\large \FTPL}\\
 \begin{tabular}[t]{l|l}
 \hline\\
    {\tt Input} & 
    \begin{minipage}[t]{\probdefwidth}
      A hypergraph $\cF$ with vertex set $U$, a tree $T$ and a
      bijection $\cl$~$:$~$\cF \rightarrow \cP$, where $\cP$ is a set
      of paths from $T$.\\
    \end{minipage}\\
    {\tt Question} &
    \begin{minipage}[t]{\probdefwidth}
      Does there exist a bijection $\phi$~$:$~$U \rightarrow V(T)$
      such that $\phi$ when applied on any hyperedge in $\cF$ will
      give
      the path mapped to it by the given tree path labeling $\cl$.\\
      { i.e., $\cl(S) = \{\phi(x) \mid x \in S\}$, for every hyperedge
        $S \in \cF$.}
    \end{minipage}\\
  \end{tabular}
  % \end{singlespace}
\end{minipage}\\
}
%\end{tabular}

@@

Aside from checking if a given TPL is feasible, we also solve the
problem of computing a feasible TPL for a given hypergraph and target
tree, if one exists. This problem, {\CFTPL}, is defined as follows.

{\small
\begin{minipage}[h]{5in}
 % \begin{singlespace}
 \vspace{2mm}
  {\large \CFTPL}\\
  % 
  \begin{tabular}[t]{l|l}
    \hline\\
    {\tt Input} & 
    \begin{minipage}[t]{\probdefwidth}
      A hypergraph $\cF$ with vertex set $U$ and a tree $T$.\\
    \end{minipage}\\

    {\tt Question} &
    \begin{minipage}[t]{\probdefwidth}
      Does there exist a set of paths $\cP$ from $T$ and a bijection
      $\cl$~$:$~$\cF \rightarrow \cP$, such that {\FTPL} returns {\bf
        true} on $(\cF, T, \cl)$.
    \end{minipage}\\
  \end{tabular}
  % \end{singlespace}
\end{minipage}\\
}
\def \CFTPLKTREE {\sc Compute $k$-subdivided Star Path Labeling}

We present a polynomial time algorithm for {\CFTPL} when the target
tree $T$ belongs to a special class of trees called {\em
  $k$-subdivided stars} and when the hyperedges in the hypergraph
$\cF$ have at most $k+2$ vertices. The examples of $k$-subdivided
stars are given in Figure~\ref{fig:ksubstar}.

%This problem, {\CFTPLKTREE}, is defined as follows. \\
\begin{figure}[t]
  \centering
  \begin{tabular}[h]{ccccc}
  \includegraphics[scale=0.3]{../img/star.pdf} &&&&
  \includegraphics[scale=0.3]{../img/kstar.pdf}\\
  (a) &&&& (b)
  \end{tabular}
  \caption{\figtabsize Examples of $k$-subdivided stars. (a) $k = 0$
    (b) $k = 2$ }
  \label{fig:ksubstar}
\end{figure}

%\vspace{3mm}
{\small
\begin{minipage}[h]{5in}
 % \begin{singlespace}
 \vspace{2mm}
  {\large \CFTPLKTREE}\\
  \begin{tabular}[t]{l|l}
    \hline\\
    {\tt Input} & 
    \begin{minipage}[t]{\probdefwidth}
      A hypergraph $\cF$ with vertex set $U$ such that every hyperedge
      $S \in \cF$ is of cardinality atmost $k+2$ and a $k$-subdivided
      star $T$.\\
    \end{minipage}\\
    {\tt Question} &
    \begin{minipage}[t]{\probdefwidth}
      Does there exist a set of paths $\cP$ from $T$ and a bijection
      $\cl$~$:$~$\cF \rightarrow \cP$, such that {\FTPL} returns {\bf
        true} on $(\cF, T, \cl)$.
    \end{minipage}\\
  \end{tabular}
  % \end{singlespace}
\end{minipage}\\
}

In spite of this being a restricted case, we believe that our results
are of significant interest in understanding the nature of {\sc Graph
  Isomorphism} which is polynomial time solvable in interval graphs
while being hard on path graphs\cite{kklv10}.
